\documentclass[a4paper,10pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{array}

\geometry{margin=0.65in}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{3pt}
\setlist[itemize]{leftmargin=*, topsep=2pt, itemsep=2pt}

\newcommand{\resheading}[1]{\vspace{8pt}\textbf{\large #1}\par\hrule\vspace{4pt}}

\begin{document}

\begin{center}
{\LARGE \textbf{SARANG S}}\\
Alappuzha, Kerala, India \quad | \quad +91 7511133612 \quad | \quad \href{mailto:sarangsvkm@gmail.com}{sarangsvkm@gmail.com}\\
\href{https://github.com/sarangsvkm}{github.com/sarangsvkm} \quad | \quad
\href{https://linkedin.com/in/sarangsvkm}{linkedin.com/in/sarangsvkm} \quad | \quad
\href{https://sarangsvkm.in}{sarangsvkm.in}
\end{center}

\resheading{Professional Summary}
Java Backend Developer with 2+ years of experience building scalable business applications using Java, Spring Boot, PostgreSQL, and React.js. Strong background in ERP development, REST API design, RBAC security, reporting, and backend performance optimization for real-world enterprise workflows.

\resheading{Technical Skills}
\begin{tabular}{>{\raggedright\arraybackslash}p{2.3cm} p{13.2cm}}
\textbf{Languages} & Java, Python, SQL \\
\textbf{Frameworks} & Spring Boot, React.js, JSP \\
\textbf{Backend} & REST APIs, JDBC, JSON, Microservices, RBAC, JasperReports \\
\textbf{Databases} & PostgreSQL, MySQL \\
\textbf{Tools} & Git, Postman, Eclipse IDE, DBeaver \\
\textbf{Concepts} & Backend Architecture, Query Optimization, Enterprise Workflows, Data Structures, Algorithms \\
\end{tabular}

\resheading{Experience}
\textbf{Software Developer} \hfill Aug 2023 -- Present\\
Blogtec Software LLP, Kochi, Kerala
\begin{itemize}
\item Developed and maintained jewellery ERP software supporting billing, inventory management, sales workflows, and reporting.
\item Designed and implemented RESTful APIs using Java and Spring Boot with PostgreSQL-backed business modules.
\item Implemented role-based access control to strengthen application security and user-level permissions.
\item Optimized SQL queries and backend flows to improve responsiveness and operational performance.
\item Built operational and financial reporting modules using JasperReports for day-to-day business monitoring.
\item Collaborated with cross-functional teams to deliver scalable features across enterprise management platforms.
\end{itemize}

\textbf{Full Stack Developer Intern} \hfill Oct 2022 -- Mar 2023\\
Kompetenzen Technologies, Kochi
\begin{itemize}
\item Developed web modules using Java, JSP, HTML, CSS, and SQL.
\item Supported backend development and database integration for application modules.
\end{itemize}

\textbf{Python Full Stack Developer Intern} \hfill Sep 2022 -- Dec 2022\\
Inmakes Learning Hub, Kochi
\begin{itemize}
\item Developed web applications using Python, HTML, CSS, and SQL.
\item Implemented backend logic and integrated database-driven features.
\end{itemize}

\resheading{Projects}
\textbf{Aurix ERP -- Jewellery Management System}
\begin{itemize}
\item Developed ERP modules for billing, inventory management, barcode tracking, credit purchase workflows, and daily sales calculations.
\item Generated financial and operational reports using JasperReports to support business operations.
\end{itemize}

\textbf{AurixWeb -- Web ERP Application}
\begin{itemize}
\item Built a web-based ERP platform using Spring Boot and PostgreSQL for item, sales, and customer management.
\item Delivered backend modules and APIs for core business workflows in a browser-based experience.
\end{itemize}

\textbf{Payroll and HR Management System}
\begin{itemize}
\item Developed employee management and payroll processing modules for HR operations.
\item Implemented employee record maintenance and HR policy tracking features.
\end{itemize}

\resheading{Education}
\textbf{Bachelor of Technology in Computer Science and Engineering} \hfill 2018 -- 2022\\
Mahaguru Institute of Technology, Kayamkulam\\
Affiliated to APJ Abdul Kalam Technological University\\
Credit Transfer: North East Frontier Technical University (Dec 2024)

\resheading{Certifications}
Introduction to Python, PostgreSQL Developer, JavaFX, Architecting with Google Compute Engine

\resheading{Languages}
English, Malayalam

\end{document}
